# Data transformation

## Select Data

The original data includes the records which is more than one year, so we firstly choose the data between end of April last year to the beginning of May 2022.

```{r}
BTC<-BTC[(nrow(BTC)-370):(nrow(BTC)-4),]
BNB<-BNB[(nrow(BNB)-370):(nrow(BNB)-4),]
ETH<-ETH[(nrow(ETH)-370):(nrow(ETH)-4),]
USDC<-USDC[(nrow(USDC)-370):(nrow(USDC)-4),]
USDT<-USDT[(nrow(USDT)-370):(nrow(USDT)-4),]
```

## Combine the Data

we will combine the price of each cryptocurrency into one table df.close

```{r}
df.close<-data.frame(cbind(BTC[,1],BTC[,2],BNB[,2],ETH[,2],USDC[,2],USDT[,2]))
colnames(df.close)<-c("Date","BTC","BNB","ETH","USDC","USDT")
head(df.close)
```

Here, we transform the table df.close into the new table df.close1 which will be helpful for plotting. 

```{r}
df.close1<- gather(df.close[,2:6], cryptocurrency, price)
df.close1$price<-as.numeric(df.close1$price)
head(df.close1)
```

## Calculate the Return and Volatility

Firstly, we calculate the return of each date by the formula: (final price/ initial price)-1.  
Then we calculate the 15 days volatility of each crypto by   calculating the stand deviation of 15 days return, and multiply square root of 365. (For stocks, the volatility is stand deviation multiply square root of 250, but the cryptocurrency can be traded every day, so we choose square root of 365 )

```{r}
# volatility
BTC$Return<-NA
for (i in 2:nrow(BTC)){
  BTC$Return[i]<-(BTC$price[i]/BTC$price[i-1])-1
}

BTC$Vol<-NA
for (i in 16:nrow(BTC)){
  BTC$Vol[i]<-sd(c(BTC$Return[i-14],BTC$Return[i-13],BTC$Return[i-12],
                   BTC$Return[i-11],BTC$Return[i-10],BTC$Return[i-9],
                   BTC$Return[i-8],BTC$Return[i-7],BTC$Return[i-6],
                   BTC$Return[i-5],BTC$Return[i-4],BTC$Return[i-3],
                   BTC$Return[i-2],BTC$Return[i-1],BTC$Return[i]))*sqrt(365)
}

```
```{r}
BNB$Return<-NA
for (i in 2:nrow(BNB)){
  BNB$Return[i]<-(BNB$price[i]/BNB$price[i-1])-1
}

BNB$Vol<-NA
for (i in 16:nrow(BNB)){
  BNB$Vol[i]<-sd(c(BNB$Return[i-14],BNB$Return[i-13],BNB$Return[i-12],
                   BNB$Return[i-11],BNB$Return[i-10],BNB$Return[i-9],
                   BNB$Return[i-8],BNB$Return[i-7],BNB$Return[i-6],
                   BNB$Return[i-5],BNB$Return[i-4],BNB$Return[i-3],
                   BNB$Return[i-2],BNB$Return[i-1],BNB$Return[i]))*sqrt(365)
}
```
```{r}
ETH$Return<-NA
for (i in 2:nrow(ETH)){
  ETH$Return[i]<-(ETH$price[i]/ETH$price[i-1])-1
}

ETH$Vol<-NA
for (i in 16:nrow(ETH)){
  ETH$Vol[i]<-sd(c(ETH$Return[i-14],ETH$Return[i-13],ETH$Return[i-12],
                   ETH$Return[i-11],ETH$Return[i-10],ETH$Return[i-9],
                   ETH$Return[i-8],ETH$Return[i-7],ETH$Return[i-6],
                   ETH$Return[i-5],ETH$Return[i-4],ETH$Return[i-3],
                   ETH$Return[i-2],ETH$Return[i-1],ETH$Return[i]))*sqrt(365)
}
```
```{r}
USDC$Return<-NA
for (i in 2:nrow(USDC)){
  USDC$Return[i]<-(USDC$price[i]/USDC$price[i-1])-1
}

USDC$Vol<-NA
for (i in 16:nrow(USDC)){
  USDC$Vol[i]<-sd(c(USDC$Return[i-14],USDC$Return[i-13],USDC$Return[i-12],
                   USDC$Return[i-11],USDC$Return[i-10],USDC$Return[i-9],
                   USDC$Return[i-8],USDC$Return[i-7],USDC$Return[i-6],
                   USDC$Return[i-5],USDC$Return[i-4],USDC$Return[i-3],
                   USDC$Return[i-2],USDC$Return[i-1],USDC$Return[i]))*sqrt(365)
}
```
```{r}
USDT$Return<-NA
for (i in 2:nrow(USDT)){
  USDT$Return[i]<-(USDT$price[i]/USDT$price[i-1])-1
}

USDT$Vol<-NA
for (i in 16:nrow(USDT)){
  USDT$Vol[i]<-sd(c(USDT$Return[i-14],USDT$Return[i-13],USDT$Return[i-12],
                   USDT$Return[i-11],USDT$Return[i-10],USDT$Return[i-9],
                   USDT$Return[i-8],USDT$Return[i-7],USDT$Return[i-6],
                   USDT$Return[i-5],USDT$Return[i-4],USDT$Return[i-3],
                   USDT$Return[i-2],USDT$Return[i-1],USDT$Return[i]))*sqrt(365)
}
```

## Combine All the Value into One table

Finally, we combine the volatility, return, and market capitalization and volume with the df.close1, creating the final table df.crpyto

```{r}
df.close1$Date<-rep(df.close$Date,5)
df.crypto<-
  cbind(df.close1,
        market_cap=c(BTC$market_cap,BNB$market_cap,ETH$market_cap,
                     USDC$market_cap,USDT$market_cap),
        return=c(BTC$Return,BNB$Return,ETH$Return,USDC$Return,USDT$Return),
        volatility=c(BTC$Vol,BNB$Vol,ETH$Vol,USDC$Vol,USDT$Vol),
        volume=c(BTC$total_volume,BNB$total_volume,ETH$total_volume,
                     USDC$total_volume,USDT$total_volume))
df.crypto$Date<-as.Date(df.crypto$Date)
df.crypto$year <- strftime(df.crypto$Date, "%Y")    # Create year column
df.crypto$month <- strftime(df.crypto$Date, "%m")
head(df.crypto)
```


